---
title: "07 08 2020 - HR Leaders"
author: "Brett Moxham"
date: "08/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r}
library(tidyverse)
library(Lahman)
```


## Creating our data frame.

The data from Sean Lahman is excellent. But for our requirments, it will require some fine tuning. The first time i attempted this I made a rookie mistake, but not verifying the data was correct for what i needed. 

```{r}
years <- Batting %>% 
  select(yearID) %>% 
  distinct()

playerInfo %>% 
  select(playerID, nameFirst, nameLast)

players <-  Batting %>% 
  select(playerID) %>% 
  distinct() %>% 
  left_join(
    People %>% 
      select(playerID, nameFirst, nameLast)
  ) %>% 
  mutate(full_name = paste0(nameFirst, " ", nameLast))


player_year_combi <- merge(players, years) 


hr_full <-as_tibble(Batting %>% 
  select(playerID, yearID, HR) %>% 
  right_join(player_year_combi, by = c("playerID", "yearID"))) %>% 
  mutate(HR = coalesce(HR, as.integer(0)))

```


## Create a rolling rank.

```{r}
hr_ranked <- hr_full %>% 
  arrange(playerID,yearID) %>% 
  group_by(playerID) %>% 
  mutate(hr_total = cumsum(HR)) %>% 
  ungroup() %>% 
  group_by(yearID) %>% 
  mutate(rank_hr = rank(-hr_total, ties.method = "first")*1,
         value_rel = hr_total/hr_total[rank_hr == 1],
         value_label = paste0(" ", hr_total)) %>% 
  filter(rank_hr <= 10) %>% 
  ungroup()

```
My first attempt at creating a rank went poorly. I kept wracking my head as to why my plots weren't working. It's because our entries don't track all the way through to 2019. For instance ```r playerID``` ```r abercda01``` only has an entry for the year ```r 1871```. I need to find a way to fill out the ```rplayerID``` and ```r yearID``` all the way through to 2019 and back to 1871. The above is my attempt to work through my issue. I followed the race chart example from [here](https://towardsdatascience.com/how-to-do-that-animated-race-bar-chart-57f3a8ff27a8) and [here](https://www.r-bloggers.com/how-to-create-bar-race-animation-charts-in-r/) as a way to build the plot, and work through the required variables for the rankings. 

## Plot


```{r}
p <- hr_ranked %>% 
  #filter(yearID>=2015,
         #yearID<= 2019) %>% 
  ggplot(aes(rank_hr))+
  geom_tile(aes(y = hr_total/2,
               height = hr_total,
               width = 0.8,
               fill = full_name, 
               color = full_name,
               alpha = 0.8)) +
  geom_text(aes(y = 0, label = paste(full_name, " "), size = 12, vjust = 0.2, hjust = 1))+
  geom_text(aes(y = hr_total, label = value_label, hjust = 0))+
  coord_flip(clip = "off", expand = FALSE)+
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse()+
  guides(fill = FALSE, color = FALSE, size = FALSE, alpha = FALSE)+
  theme_void()+
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
         legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.2, color="grey" ),
        panel.grid.minor.x = element_line( size=.2, color="grey" ),
        plot.title=element_text(size=25, hjust=0.5, face="bold", colour="grey", vjust=1),
        plot.subtitle=element_text(size=16, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=10, hjust=0, face="italic", color="grey"),
        plot.background=element_blank(),
        plot.margin = margin(2,2,2,4, "cm"))
   

  
  
p_anim <- p  +
  gganimate::transition_states(yearID, transition_length = .2, state_length = .5)+
  #gganimate::view_follow(fixed_x = TRUE)+
  gganimate::ease_aes("cubic-in-out")+
  labs(title = "Home Run Leaders Over the Years",
      subtitle = "{closest_state}",
      caption = "@bmoxO9 | Source: Lahman Database | #100DaysofCode"
)



gganimate::animate(p_anim,
                   nframes = 100,
                   duration = 100,
                   fps = 15,
                   width = 1280,
                   height = 720,
                   renderer = gganimate::gifski_renderer("gifs/HR_race.gif"),
                   start_pause = 4,
                   end_pause = 5)

```







